### 2020-09-25 submission/manuscript.tex
Remove figures from manuscript, prepare files for submitting revision

\includegraphics{figure_1.pdf} \textbf{Figure 1. Microbiota variation is
high between mice from different sources.} A-B. Number of observed OTUs
(A) and Shannon diversity index values (B) across sources of mice at
baseline (day -1 of the experiment). Differences between sources were
analyzed by Kruskal-Wallis test with Benjamini-Hochberg correction for
testing each day of the experiment and the adjusted \emph{P} value was
\textless{} 0.05 for panel A (Table S1). None of the \emph{P} values
from pairwise Wilcoxon comparisons between sources were significant
after Benjamini-Hochberg correction (Table S2). Gray lines represent the
median values for each source of mice. C. Principal Coordinates Analysis
(PCoA) of \(\theta_{YC}\) distances of baseline stool samples. Source
and the interaction between source and cage effects explained most of
the variation (PERMANOVA combined R\textsuperscript{2} = 0.90, \emph{P}
\textless{} 0.001; Table S3). For A-C: each symbol represents the value
for a stool sample from an individual mouse, circles represent
experiment 1 mice and triangles represent experiment 2 mice. D. The
median (point) and interquantile range (colored lines) of the relative
abundances for the 20 most significant OTUs out of the 268 OTUs that
varied across sources at baseline by Kruskal-Wallis test with
Benjamini-Hochberg correction (Table S5).

@@

\includegraphics{figure_2.pdf}

@@

\includegraphics{figure_3.pdf} \textbf{Figure 3. Clindamycin treatment
alters bacteria in all sources, but a subset of bacterial differences
across sources persists.} A-B. Number of observed OTUs (A) and Shannon
diversity index values (B) across sources of mice after clindamycin
treatment (day 0). Differences between sources were analyzed by
Kruskal-Wallis test with Benjamini-Hochberg correction for testing each
day of the experiment and the adjusted \emph{P} value was \textless{}
0.05 (Table S1). Significant \emph{P} values from the pairwise Wilcoxon
comparisons between sources with Benjamini-Hochberg correction are
displayed as the first initial of each group compared to the group that
they are listed above (Table S2). C. PCoA of \(\theta_{YC}\) distances
from stools collected post-clindamycin. Source and the interaction
between source and cage effects explained most of the variation observed
post-clindamycin (PERMANOVA combined R\textsuperscript{2} = 0.99,
\emph{P} \textless{} 0.001; Table S3). For A-C, each symbol represents a
stool sample from an individual mouse, with circles representing
experiment 1 mice and triangles representing experiment 2 mice. D. The
median (point) and interquantile range (colored lines) of the relative
abundances for the 18 OTUs (Table S8) that varied between sources after
clindamycin treatment (day 0). E. The median (point) and interquantile
range (colored lines) of the top 10 most significant OTUs out of 153
with relative abundances that changed because of the clindamycin
treatment (adjusted \emph{P} value \textless{} 0.05). Data were analyzed
by paired Wilcoxon signed rank test of mice that had paired sequence
data for baseline (day -1) and post-clindamycin (day 0) timepoints (N =
31), with Benjamini-Hochberg correction for testing all identified OTUs
(Table S9). The gray vertical line indicates the limit of detection.

@@

\includegraphics{figure_4.pdf} \textbf{Figure 4. Microbiota variation
across sources is maintained after \emph{C. difficile} challenge.} A-B.
Number of observed OTUs (A) and Shannon diversity index values (B)
across sources of mice 1-day post-infection. Data were analyzed by
Kruskal-Wallis test with Benjamini-Hochberg correction for testing each
day of the experiment and the adjusted \emph{P} value was \textless{}
0.05 (Table S1). Significant \emph{P} values from the pairwise Wilcoxon
comparisons between sources with Benjamini-Hochberg correction are
displayed as the first initial of each group compared to the group that
they are listed above (Table S2). PCoA of \(\theta_{YC}\) distances of
1-day post-infection stool samples. Source and the interaction between
source and cage effects explained most of the variation between fecal
communities (PERMANOVA combined R\textsuperscript{2} = 0.88, \emph{P}
\textless{} 0.001; Table S3). For A-C: each symbol represents the value
for a stool sample from an individual mouse, circles represent
experiment 1 mice and triangles represent experiment 2 mice. D. The
median (point) and interquantile range (colored lines) of the relative
abundances for the top 20 most significant OTUs out of the 44 OTUs that
varied between sources 1-day post-infection. The gray vertical line
indicates the limit of detection. For each timepoint OTUs with
differential relative abundances across sources of mice were identified
by Kruskal-Wallis test with Benjamini-Hochberg correction for testing
all identified OTUs (Table S10). E. \(\theta_{YC}\) distances of fecal
samples collected 7-days post-infection relative to the baseline (day
-1) sample for each mouse. Each symbol represents an individual mouse.
Gray lines represent the median for each source.

@@

\includegraphics{figure_5.pdf} \textbf{Figure 5. Bacteria that
influenced whether mice cleared \emph{C. difficile} by day 7.} A.
Post-clindamycin (day 0) relative abundance data for the 10 OTUs with
the highest rankings based on feature weights in the post-clindamycin
(day 0) classification model. Red font represents OTUs that correlated
with \emph{C. difficile} colonization and blue font represents OTUs that
correlated with clearance. Symbols represent the relative abundance data
for an individual mouse. Gray bars indicate the median relative
abundances for each source. The gray horizontal lines indicate the limit
of detection. B. Venn diagram that combines OTUs that were important to
the day -1, 0, and 1 classification models ( Fig. S4, Table S14) and
either overlapped with taxa that varied across sources at the same
timepoint, were impacted by clindamycin treatment, or both. Bold OTUs
were important to more than 1 classification model.

@@

\includegraphics{figure_6.pdf} \textbf{Figure 6: OTUs associated with
\emph{C. difficile} colonization dynamics vary across sources throughout
the experiment.} A-D. Relative abundances of bold OTUs from Fig. 5B that
were important in at least two classification models are shown over
time. A. \emph{Bacteroides} (OTU 2), which varied across sources
throughout the experiment. B-C. \emph{Enterobacteriaceae} (B) and
\emph{Enterococcus} (C), which significantly varied across sources and
were impacted by clindamycin treatment. D. \emph{Porphyromonadaceae}
(OTU 7), which was significantly impacted by clindamycin treatment and
after examining relative abundance dynamics over the course of the
experiment was found to also significantly vary between sources of mice
on days -1, 5, 6, 7, and 9 of the experiment. Symbols represent the
relative abundance data for an individual mouse. Colored lines indicate
the median relative abundances for each source. The gray horizontal line
represents the limit of detection. Timepoints where differences between
sources of mice were statistically significant by Kruskal-Wallis test
with Benjamini-Hochberg correction for testing across multiple days
(Table S15) are identified by the asterisk above each timepoint (*, P
\textless{} 0.05).

@@

\includegraphics{figure_S1.pdf}

@@

\includegraphics{figure_S2.pdf} \textbf{Figure S2. \emph{C. difficile}
CFU variation across sources varies slightly between the 2 experiments.}
A-B. \emph{C. difficile} CFU/gram of stool quantification over time for
experiment 1 (A) and 2 (B). Experiments were conducted approximately 3
months apart. Lines represent the median CFU for each source, symbols
represent individual mice and the black line represents the limit of
detection. C. \emph{C. difficile} CFU/gram stool 7-days post-infection
across sources of mice with an asterisk for pairwise Wilcoxon
comparisons with Benjamini-Hochberg correction where \emph{P}
\textless{} 0.05. D. Mouse weight change 2-days post-infection across
sources of mice, no pairwise Wilcoxon comparisons were significant after
Benjamini-Hochberg correction. For C-D: circles represent experiment 1
mice, triangles represent experiment 2 mice and gray lines indicate the
median values for each group. E. Percent of mice that were colonized
with \emph{C. difficile} over the course of the experiment. Each day the
percent is calculated based on the mice where \emph{C. difficile} CFU
was quantified for that particular day. Total N for each day: day 1 (N =
42), day 2 (N = 20), day 3 (N = 39), day 4 (N = 29), day 5 (N = 43), day
6 (N = 34), day 7 (N = 40), day 8 (N = 36), and day 9 (N = 46).

@@

\includegraphics{figure_S3.pdf} \textbf{Figure S3. Bacterial community
composition before, after clindamycin perturbation, and post-infection
can predict \emph{C. difficile} colonization status 7 days
post-infection.} A. Bar graph visualizations of overall 7-days
post-infection \emph{C. difficile} colonization status that were used as
classification outcomes to build L2-regularized logistic regression
models. Mice were classified as colonized or cleared (not detectable at
the limit of detection of 100 CFU) based on CFU g/stool data from 7 days
post-infection. B. \emph{C. difficile} CFU status on Day 7 within each
mouse source. N = 8-9 mice per group. C. L2-regularized logistic
regression classification model area under the receiving operator
characteristic curve (AUROCs) to predict \emph{C. difficile} CFU on day
7 post-infection (Fig. 2B, Fig. S2C) based on the OTU community relative
abundances at baseline (day -1), post-clindamycin (day 0), and 1-day
post-infection. All models performed better than random chance (AUROC =
0.5, all \emph{P} \textless{} 0.001, Table S12) and the model built with
post-clindamycin bacterial OTU relative abundances had the best
performance ((\emph{P}\textsubscript{FDR} \textless{} 0.001 for all
pairwise comparisons, Table S13). See Table S14 for list of the 20 OTUs
that were ranked as most important to each model.

@@

\includegraphics{figure_S4.pdf}

>>>>

\textbf{Figure 1. Microbiota variation is high between mice from
different sources.} A-B. Number of observed OTUs (A) and Shannon
diversity index values (B) across sources of mice at baseline (day -1 of
the experiment). Differences between sources were analyzed by
Kruskal-Wallis test with Benjamini-Hochberg correction for testing each
day of the experiment and the adjusted \emph{P} value was \textless{}
0.05 for panel A (Table S1). None of the \emph{P} values from pairwise
Wilcoxon comparisons between sources were significant after
Benjamini-Hochberg correction (Table S2). Gray lines represent the
median values for each source of mice. C. Principal Coordinates Analysis
(PCoA) of \(\theta_{YC}\) distances of baseline stool samples. Source
and the interaction between source and cage effects explained most of
the variation (PERMANOVA combined R\textsuperscript{2} = 0.90, \emph{P}
\textless{} 0.001; Table S3). For A-C: each symbol represents the value
for a stool sample from an individual mouse, circles represent
experiment 1 mice and triangles represent experiment 2 mice. D. The
median (point) and interquantile range (colored lines) of the relative
abundances for the 20 most significant OTUs out of the 268 OTUs that
varied across sources at baseline by Kruskal-Wallis test with
Benjamini-Hochberg correction (Table S5).

@@

@@

\textbf{Figure 3. Clindamycin treatment alters bacteria in all sources,
but a subset of bacterial differences across sources persists.} A-B.
Number of observed OTUs (A) and Shannon diversity index values (B)
across sources of mice after clindamycin treatment (day 0). Differences
between sources were analyzed by Kruskal-Wallis test with
Benjamini-Hochberg correction for testing each day of the experiment and
the adjusted \emph{P} value was \textless{} 0.05 (Table S1). Significant
\emph{P} values from the pairwise Wilcoxon comparisons between sources
with Benjamini-Hochberg correction are displayed as the first initial of
each group compared to the group that they are listed above (Table S2).
C. PCoA of \(\theta_{YC}\) distances from stools collected
post-clindamycin. Source and the interaction between source and cage
effects explained most of the variation observed post-clindamycin
(PERMANOVA combined R\textsuperscript{2} = 0.99, \emph{P} \textless{}
0.001; Table S3). For A-C, each symbol represents a stool sample from an
individual mouse, with circles representing experiment 1 mice and
triangles representing experiment 2 mice. D. The median (point) and
interquantile range (colored lines) of the relative abundances for the
18 OTUs (Table S8) that varied between sources after clindamycin
treatment (day 0). E. The median (point) and interquantile range
(colored lines) of the top 10 most significant OTUs out of 153 with
relative abundances that changed because of the clindamycin treatment
(adjusted \emph{P} value \textless{} 0.05). Data were analyzed by paired
Wilcoxon signed rank test of mice that had paired sequence data for
baseline (day -1) and post-clindamycin (day 0) timepoints (N = 31), with
Benjamini-Hochberg correction for testing all identified OTUs (Table
S9). The gray vertical line indicates the limit of detection.

@@

\textbf{Figure 4. Microbiota variation across sources is maintained
after \emph{C. difficile} challenge.} A-B. Number of observed OTUs (A)
and Shannon diversity index values (B) across sources of mice 1-day
post-infection. Data were analyzed by Kruskal-Wallis test with
Benjamini-Hochberg correction for testing each day of the experiment and
the adjusted \emph{P} value was \textless{} 0.05 (Table S1). Significant
\emph{P} values from the pairwise Wilcoxon comparisons between sources
with Benjamini-Hochberg correction are displayed as the first initial of
each group compared to the group that they are listed above (Table S2).
PCoA of \(\theta_{YC}\) distances of 1-day post-infection stool samples.
Source and the interaction between source and cage effects explained
most of the variation between fecal communities (PERMANOVA combined
R\textsuperscript{2} = 0.88, \emph{P} \textless{} 0.001; Table S3). For
A-C: each symbol represents the value for a stool sample from an
individual mouse, circles represent experiment 1 mice and triangles
represent experiment 2 mice. D. The median (point) and interquantile
range (colored lines) of the relative abundances for the top 20 most
significant OTUs out of the 44 OTUs that varied between sources 1-day
post-infection. The gray vertical line indicates the limit of detection.
For each timepoint OTUs with differential relative abundances across
sources of mice were identified by Kruskal-Wallis test with
Benjamini-Hochberg correction for testing all identified OTUs (Table
S10). E. \(\theta_{YC}\) distances of fecal samples collected 7-days
post-infection relative to the baseline (day -1) sample for each mouse.
Each symbol represents an individual mouse. Gray lines represent the
median for each source.

@@

\textbf{Figure 5. Bacteria that influenced whether mice cleared \emph{C.
difficile} by day 7.} A. Post-clindamycin (day 0) relative abundance
data for the 10 OTUs with the highest rankings based on feature weights
in the post-clindamycin (day 0) classification model. Red font
represents OTUs that correlated with \emph{C. difficile} colonization
and blue font represents OTUs that correlated with clearance. Symbols
represent the relative abundance data for an individual mouse. Gray bars
indicate the median relative abundances for each source. The gray
horizontal lines indicate the limit of detection. B. Venn diagram that
combines OTUs that were important to the day -1, 0, and 1 classification
models ( Fig. S4, Table S14) and either overlapped with taxa that varied
across sources at the same timepoint, were impacted by clindamycin
treatment, or both. Bold OTUs were important to more than 1
classification model.

@@

\textbf{Figure 6: OTUs associated with \emph{C. difficile} colonization
dynamics vary across sources throughout the experiment.} A-D. Relative
abundances of bold OTUs from Fig. 5B that were important in at least two
classification models are shown over time. A. \emph{Bacteroides} (OTU
2), which varied across sources throughout the experiment. B-C.
\emph{Enterobacteriaceae} (B) and \emph{Enterococcus} (C), which
significantly varied across sources and were impacted by clindamycin
treatment. D. \emph{Porphyromonadaceae} (OTU 7), which was significantly
impacted by clindamycin treatment and after examining relative abundance
dynamics over the course of the experiment was found to also
significantly vary between sources of mice on days -1, 5, 6, 7, and 9 of
the experiment. Symbols represent the relative abundance data for an
individual mouse. Colored lines indicate the median relative abundances
for each source. The gray horizontal line represents the limit of
detection. Timepoints where differences between sources of mice were
statistically significant by Kruskal-Wallis test with Benjamini-Hochberg
correction for testing across multiple days (Table S15) are identified
by the asterisk above each timepoint (*, P \textless{} 0.05).

@@

@@

\textbf{Figure S2. \emph{C. difficile} CFU variation across sources
varies slightly between the 2 experiments.} A-B. \emph{C. difficile}
CFU/gram of stool quantification over time for experiment 1 (A) and 2
(B). Experiments were conducted approximately 3 months apart. Lines
represent the median CFU for each source, symbols represent individual
mice and the black line represents the limit of detection. C. \emph{C.
difficile} CFU/gram stool 7-days post-infection across sources of mice
with an asterisk for pairwise Wilcoxon comparisons with
Benjamini-Hochberg correction where \emph{P} \textless{} 0.05. D. Mouse
weight change 2-days post-infection across sources of mice, no pairwise
Wilcoxon comparisons were significant after Benjamini-Hochberg
correction. For C-D: circles represent experiment 1 mice, triangles
represent experiment 2 mice and gray lines indicate the median values
for each group. E. Percent of mice that were colonized with \emph{C.
difficile} over the course of the experiment. Each day the percent is
calculated based on the mice where \emph{C. difficile} CFU was
quantified for that particular day. Total N for each day: day 1 (N =
42), day 2 (N = 20), day 3 (N = 39), day 4 (N = 29), day 5 (N = 43), day
6 (N = 34), day 7 (N = 40), day 8 (N = 36), and day 9 (N = 46).

@@

\textbf{Figure S3. Bacterial community composition before, after
clindamycin perturbation, and post-infection can predict \emph{C.
difficile} colonization status 7 days post-infection.} A. Bar graph
visualizations of overall 7-days post-infection \emph{C. difficile}
colonization status that were used as classification outcomes to build
L2-regularized logistic regression models. Mice were classified as
colonized or cleared (not detectable at the limit of detection of 100
CFU) based on CFU g/stool data from 7 days post-infection. B. \emph{C.
difficile} CFU status on Day 7 within each mouse source. N = 8-9 mice
per group. C. L2-regularized logistic regression classification model
area under the receiving operator characteristic curve (AUROCs) to
predict \emph{C. difficile} CFU on day 7 post-infection (Fig. 2B, Fig.
S2C) based on the OTU community relative abundances at baseline (day
-1), post-clindamycin (day 0), and 1-day post-infection. All models
performed better than random chance (AUROC = 0.5, all \emph{P}
\textless{} 0.001, Table S12) and the model built with post-clindamycin
bacterial OTU relative abundances had the best performance
((\emph{P}\textsubscript{FDR} \textless{} 0.001 for all pairwise
comparisons, Table S13). See Table S14 for list of the 20 OTUs that were
ranked as most important to each model.

@@
